\begin{enumerate}[leftmargin=1.5em, itemsep=0.3em, label={[\arabic*]}]
    \item \textbf{Jie Gao}, Kenny Tsu Wei Choo, Junming Cao, Roy Ka-Wei Lee, and Simon Perrault. CoAICoder: Examining the effectiveness of AI-assisted human-to-human collaboration in qualitative analysis. \emph{ACM Transaction on Computer Human Interaction (TOCHI)}, 2023. \url{https://doi.org/10.1145/3617362}.
    
    \item \textbf{Jie Gao}, Yuchen Guo, Gionnieve Lim, Tianqin Zhang, Zheng Zhang, Toby Jia-Jun Li, and Simon Tangi Perrault. CollabCoder: A lower-barrier, rigorous workflow for inductive collaborative qualitative analysis with large language models. In \emph{Proceedings of the 2024 CHI Conference on Human Factors in Computing Systems (CHI24)}, 2024. \url{https://doi.org/10.1145/3613904.3642002}.

    
    \item \textbf{Jie Gao}, Yue Xue, Xiaofei Xie, SoeMin Thant, Erika Lee, and Bowen Xu. Understanding codebase like a professional! Human-AI collaboration for code comprehension, 2026. \url{https://arxiv.org/abs/2504.04553}. Accepted at the 34th IEEE/ACM International Conference on Program Comprehension (ICPC 2026).

    \item \textbf{Jie Gao}, Simret Araya Gebreegziabher, Kenny Tsu Wei Choo, Toby Jia-Jun Li, Simon Tangi Perrault, and Thomas W Malone. A taxonomy for human-LLM interaction modes: An initial exploration. In \emph{Extended Abstracts of the CHI Conference on Human Factors in Computing Systems}, CHI EA '24. \url{https://doi.org/10.1145/3613905.3650786}.

    \item \textbf{Jie Gao}, Xiayin Ying, Junming Cao, Yifan Yang, Pin Sym Foong, and Simon Perrault. Differences of challenges of working from home (WFH) between Weibo and Twitter users during COVID-19. In \emph{Extended Abstracts of the 2022 CHI Conference on Human Factors in Computing Systems}, CHI EA '22, 2022. \url{https://doi.org/10.1145/3491101.3519790}.

    \item \textbf{Jie Gao}, Zhiyao Shu, Shun Yi Yeo, Alok Prakash, Chien-Ming Huang, Mark Dredze, and Ziang Xiao. Efficiency with rigor! A trustworthy LLM-powered workflow for qualitative data analysis, 2025. \url{https://arxiv.org/abs/2501.00775}. \noindent\colorbox{accentcolor}{\textbf{\textcolor{white}{In submission.}}}

     \item \textbf{Jie Gao}, Thomas Malone, et al. Not just prompt engineering: A taxonomy for human LLM interaction modes, 2025. \noindent\colorbox{accentcolor}{\textbf{\textcolor{white}{In preparation.}}}
    
    \item \textbf{Jie Gao}, Mian Zhong, Jonathan Ivey, Chien Ming Huang, Ziang Xiao, and Mark Dredze. Evaluation framework for LLM assisted qualitative data analysis, 2025. \noindent\colorbox{accentcolor}{\textbf{\textcolor{white}{In preparation.}}}

     \item Zheng Zhang, \textbf{Jie Gao}, Ranjodh Singh Dhaliwal, and Toby Jia-Jun Li. VISAR: A human-AI argumentative writing assistant with visual programming and rapid draft prototyping. In \emph{Proceedings of the 36th Annual ACM Symposium on User Interface Software and Technology}, UIST '23, 2023. \url{https://doi.org/10.1145/3586183.3606800}.

      \item ShunYi Yeo, Gionnieve Lim, \textbf{Jie Gao}, Weiyu Zhang, and Simon Tangi Perrault. Help me reflect: Leveraging self-reflection interface nudges to enhance deliberativeness on online deliberation platforms. In \emph{Proceedings of the 2024 CHI Conference on Human Factors in Computing Systems}, CHI '24, 2024. \url{https://doi.org/10.1145/3613904.3642530}.
    
    \item Marianne Aubin Le Quéré, Hope Schroeder, Casey Randazzo, \textbf{Jie Gao}, Ziv Epstein, Simon Tangi Perrault, David Mimno, Louise Barkhuus, and Hanlin Li. LLMs as research tools: Applications and evaluations in HCI data work. In \emph{Extended Abstracts of the CHI Conference on Human Factors in Computing Systems}, CHI EA '24. \url{https://doi.org/10.1145/3613905.3636301}.

    
   
    
    \item Junming Cao, Bihuan Chen, Longjie Hu, \textbf{Jie Gao}, Kaifeng Huang, Xuezhi Song, and Xin Peng. Characterizing the complexity and its impact on testing in ML-enabled systems. In \emph{2023 IEEE International Conference on Software Maintenance and Evolution (ICSME)}. \url{https://doi.org/10.1109/ICSME58846.2023.00034}.
    
   
    
    \item Ruyuan Wan, Haonan Wang, Ting-Hao Kenneth Huang, and \textbf{Jie Gao}. From noise to nuance: Enriching subjective data annotation through qualitative analysis. In \emph{Proceedings of the Fourth Workshop on Bridging Human-Computer Interaction and Natural Language Processing (HCI+NLP)}, 2025. \url{https://aclanthology.org/2025.hcinlp-1.20/}.
\end{enumerate}